material and methods

### 2018-03-21 man/ms_1_material_methods.Rmd
updae

During the second half of the XX century, several extreme drought episodes were recorded for the Iberian Peninsula (*e.g*. 1994-1995, 1999, 2005, 2012) [@VicenteSerrano2014; @Guerreiro2017].The 2005 and 2012 drought events have been documented as two of the worst drought years in the last decades for the southern Iberian Peninsula [@GarciaHerrera2007; @Gouveia2014 @Gouveia2015; @Trigo2013; @Guerreiro2017; @Pascoa2017] and they were charecterized as extreme drought in our climatic data (Appendices S1-S3). We focused on these two drought events because limitations about temporal availability of high-spatial resolution remote sensing information (MODIS started on 2000; see below). Nevertheless, for radial growth-time series, older drought events were also analyzed to contextualize results obtained in 2005 and 2012 drought events. The identification of a drought event were done using the Standardized Precipitation-Evapotranspiration Index (SPEI) [@VicenteSerrano2010] following similar procedure as proposed by @Pascoa2017 (see Appendix S3)

>>>>

During the second half of the XX century, several extreme drought episodes were recorded for the Iberian Peninsula (*e.g*. 1994-1995, 1999, 2005, 2012) [@VicenteSerrano2014; @Guerreiro2017].The 2005 and 2012 drought events have been documented as two of the worst drought years in the last decades for the southern Iberian Peninsula [@GarciaHerrera2007; @Gouveia2014 @Gouveia2015; @Trigo2013; @Guerreiro2017; @Pascoa2017] and they were charecterized as extreme drought in our climatic data (Appendices S1-S3). We focused on these two drought events because limitations about temporal availability of high-spatial resolution remote sensing information (MODIS started on 2000; see below). Nevertheless, for radial growth-time series, older drought events were also analyzed to contextualize results obtained in 2005 and 2012 drought events. The identification of a drought event were done using the Standardized Precipitation-Evapotranspiration Index (SPEI) [@VicenteSerrano2010] following similar procedure as proposed by Spinioni (see Appendix S3)
